Balsa: A Compact Line Notation Based on SMILES

### 2022-07-31 manuscript.tex
Removes references to Left and Right atom parity variants. Closes #39
Adds closing angle bracket. Closes #40

The \ttt{parity} attribute of a bracket atom is determined by the \ttt{<parity>} non-terminal. Allowed values are \enquote{@} and \enquote{@@,} corresponding to the values \ttt{Left} and \ttt{Right}, respectively.

@@

The \ttt{hydrogens} attribute of a bracket atom is controlled by the \\ \ttt{<virtual{\_}hydrogen>} non-terminal. It is comprised of the terminal \enquote{H} followed by an optional \ttt{<nonzero>} non-terminal. A digit appearing after the \enquote{H} terminal sets \ttt{hydrogens} to the corresponding virtual hydrogen count. If no digit is present, \ttt{hydrogens} is set to one. The virtual hydrogen count is set to zero by omitting the \ttt{<virtual{\_}hydrogen} non-terminal.

>>>>

The \ttt{parity} attribute of a bracket atom is determined by the \ttt{<parity>} non-terminal. Allowed values are \enquote{@} and \enquote{@@,} corresponding to the values \ttt{Counterclockwise} and \ttt{Clockwise}, respectively.

@@

The \ttt{hydrogens} attribute of a bracket atom is controlled by the \\ \ttt{<virtual{\_}hydrogen>} non-terminal. It is comprised of the terminal \enquote{H} followed by an optional \ttt{<nonzero>} non-terminal. A digit appearing after the \enquote{H} terminal sets \ttt{hydrogens} to the corresponding virtual hydrogen count. If no digit is present, \ttt{hydrogens} is set to one. The virtual hydrogen count is set to zero by omitting the \ttt{<virtual{\_}hydrogen>} non-terminal.
